\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Client Meeting \#5  Minutes}\\
\end{center}
\end{adjustwidth}

Fifth Meeting (6 September 2017)
\section{Attendance:}
\textbf{Chair} - Cyrus\\
\textbf{Minute Taker} - Adam\\
\subsection*{Present}
\begin{itemize}
\item Adam Davidson, Cyrus Villacampa, Jeremy Hughes, Ravi Lam, Ziang Chen, Linlin Song
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item   James Kortman
\end {itemize}
\textbf{Meeting started at 09:22}

\section{Minutes}
\begin{enumerate}
\subsection{SPMP Presentation}
\item Cyrus - 1.1,2,3,4\\
\item Ravi - 4.1\\
\item Jeremy - 5. Risk Management.\\
\item Ravi - 6. Process Model.\\
\item Cyrus - 7. Work Plan.\\
\item Ziang - 8.1 Configuration Plan.\\
\item Adam - 8.2 Documentation Plan.\\
\item Cyrus - 8.3 Quality Assurance Plan.\\

\subsection{Feedback}
\item Comments are on submission on MyUni. 1.2 Constraints and Assumptions. Don’t repeat the SRS. The assumptions and constraints should be about actually doing the project. Don't write: The robot must be able to do this. Second half okay. First half sounds feature heavy. Talk about prototype elements. The prototype could be smaller, simpler etc.
\item Software is aimed at final product, and demo. Time and budget constraints.
\item Table 3 got a bit lost.
\item What types of risks: People, technology, hardware. When are risks monitored? The indicator doesn’t say. e.g. every meeting. Risk indicators. Severity * likelihood style table.
\item Section 6 Fine.
\item Section 7 Include WBS or diagram. You only need 3 layers. Project – GUI, Robot – Comms, etc
\item How is versioning managed? Major version each release. 
\item 8.3 Quality Assurance – Really like. When are quality reviews?
\item Configuration Management. How do you branch? Person by person. Feature by feature etc. 

\subsection{Client Meeting}
\item Milestones explained. `The robot cannot move into radioactive regions'. The robot needs to go into the radioactive region. Quite specific milestones.
\item Map demonstration. Creators are thick black lines. Only one radiation zone. The Apollo will be an obstacle. Landing tracks are when Apollo landed and skidded along the ground. NGZ missing. Vehicles can have two lines. Make it as accurate as possible. 
\item Final presentation. The client will have their own map. We should have our own as a backup. 


\vspace{.5cm}
\textbf{Meeting closed at 09:56.}\\
\end{enumerate}

\section{Action Items}
\begin{enumerate}
\item Update Map.
\item Work on Milestones.
\item Work on SPMP.
\end{enumerate}

\end{document}