\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\newcounter{qcounter}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Client Meeting \#7 Minutes}\\
\end{center}
\end{adjustwidth}


Seventh Client Meeting Minutes (3 October 2017)
\section{Attendance:}
\textbf{Chair} - Ziang\\
\textbf{Minute Taker} - Adam\\
\subsection*{Present}
\begin{itemize}
\item Adam Davidson. Cyrus Villacampa, James Kortman, Jeremy Hughes, Ravi Lam, Ziang Chen, Linlin Song
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item  
\end {itemize}

\section{Details}
\begin{itemize}
\subsection{SDD Presentation}
\item We will present the SDD. \textbf{Ravi} 1.  Introduction. \textbf{Ziang} 2. System Overview. \textbf{James} 3. System Architecture and Components Design. 4. Data Design. \textbf{Cyrus} 5. Class, State and Interaction Diagrams. \textbf{Ziang} 6. Human Interface Design. \textbf{Jeremy} Resource Estimates.
\subsection{Feedback}
\item Sensor move control in interface. Why is it there?
\item Resource Estimates. You've put hardware only, should probably include an effort estimation.\\ \textbf{Response}: The template only asked for computer resource estimates. We need to implement the resource estimate for each feature?
\item What is the design of each feature? (In XML).

\subsection{Milestone 2 Presentation}
\item Internal map isn't XML. James demonstrated.
\item Syncronisation. Jeremy demonstrated.
\item Robot movement to map destination. Cyrus demonstrated.
\item 10/10 points.
\item Some discussion on map data structure.
\item The features that need to be identified by colour are going to be a distinct colour (set) from the features we identify by shape.
\item Mystery Presentation is a boring case study which seems to serve no purpose for learning.



\end{itemize}



\end{document}