\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Client Meeting \#2  Minutes}\\
\end{center}
\end{adjustwidth}

Second Meeting (15 August 2017)
\section{Attendance:}
\textbf{Chair} - Jeremy\\
\textbf{Minute Taker} - Adam\\
\subsection*{Present}
\begin{itemize}
\item Adam Davidson, Cyrus Villacampa, James Kortman, Jeremy Hughes, Ravi Lam, Ziang Chen, Linlin Song
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item  
\end {itemize}

\section{Details:}
\begin{enumerate}
\item Can you discuss about your groups weaknesses and strengths? Have you discussed areas of strengths and weaknesses?\\
We've got more experienced programmers with experience in UI, Java and larger projects. Part of our strength is that we teach each other, coding, Eclipse, Latex.
\item Can you describe your roles?\\
Jeremy - Communication Manager - Robot assembly\\
Ziang - UI Manager - connected and functions well with Handler\\
Ravi - Testing Manager - Learning about JUnit\\
Cyrus - General Member - Co-in-charge with Ravi\\
James - Software Architecture - API communications\\
Adam - Document Manager - minutes etc - Robot movement\\
Linlin - General Member\newline

\textbf{Project Readiness:}\\
\item What is your process model?\\
Agile process model. Baseline functionality the whole way through. New information comes later, react quickly.
\item Have you picked a particular one? Scrum or Kabam or Street Programming?\\
No

\item Do you think agile fits well with the course with set dates for documentation?\\
Agile still works with dates. It's more about responding to changing requirements

\item Can you tell me about the tools you're using for code and team management?\\
We're using Eclipse for an IDE. We're using Git. We're using Discord (similar to slack). For GUI I used netbeans. As for management, we have team meetings and assign roles then. 

\item What milestones do you have?\\
For now, we're focussing on the week 6 deadline: A whole line of control from GUI to the robot. Then implement manual control, then automatic control, and then mapping. Also, finalise the robot design.

\item Can you go into detail about documentation tracking?\\
Documents are kept on Github.

\textbf{Client Meeting}\\
First item was to check minutes, but as the client changed, that didn't happen. We'll have more stable clients in the future.

\item Extra questions:
When defining the shape of a NGZ, what shape is it going to be?\\
You can start of rectangular. But then think about the restrictions of that. If you can get a rectangle to work, then that should be satisfactory.

\item GUI design questions.\\
I think it's good that there are two sections. Make it clear that it's a demonstration. Two designs: horizontal map vs vertical map. I don't have a preference to which way the map is orientated. Button choice isn't very clear. It needs to look professional. Mouse and keypress is good, but it's not a prioritiy. Make it easier for them to understand what it does. The symbols are a little bit confusing.

\item Robot design questions.\\
With the colour sensor in the middle, you'll need to make sure you're not driving on half a creator. Consider your searching algorithm.

\item Timeline for the DTD is week 6. 

\textbf{Client meeting closed}\\

Put more thought into your process. You've said agile but you didn't specify which agile model and how that ties in with documentation. Agile doesn't focus on documentation. You need to make sure everyone understands what stage you're in and what you're doing. Just do whatever, just make sure it happens. 

\end{enumerate}

\end{document}