\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Client Meeting \#4  Minutes}\\
\end{center}
\end{adjustwidth}

Fourth Meeting (29 August 2017)
\section{Attendance:}
\textbf{Chair} - Adam\\
\textbf{Minute Taker} - Ravi\\
\subsection*{Present}
\begin{itemize}
\item Adam Davidson, Cyrus Villacampa, James Kortman, Jeremy Hughes, Ravi Lam, Ziang Chen, Linlin Song
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item  
\end {itemize}
\textbf{Meeting started at 13:12}

\section{Minutes}
\begin{enumerate}
\subsection{GUI Prototype and Basic Movement Presentation}
\item GUI functionality demonstration.\\
\item Robot straight line movement tests (Forward and Backward).\\

\subsection{Q\&A}
\item Question \#1: Can the width of the window(map) be adjusted (i.e full screen)?
\\                  Not sure, since the ratio of the window is perfectly fitted with the A1 paper size, if we changed the size, it may cause data loss.
\item Question \#2: Is there any sketch of an actual physical map? Or just waiting for the DTD?
\\					Deciding, need to wait for the given colours from the example (DTD).

\subsection{Feedback:}

\item Label all the buttons (GUI)
\item Discuss and work out how accurate the actual map should be, not only based on the example (DTD).
\item Make sure the vehicle can work in different environments.
\item Do a backup
\item Bear in mind to keep the modules separated.


\subsection{Client Meeting Section}

\item Question \#1 When will the DTD ready?
\\					Week 6. It means the end of this week.



\vspace{.5cm}
\textbf{Meeting closed at 1:21.}\\
\end{enumerate}

\section{Action Items}
\begin{enumerate}
\item Start working on the Autonomous part (path finding).
\item Colour Calibration.
\item Work on hardware aspects (colour and gyro sensor) to prevent collisions.
\end{enumerate}

\end{document}