\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Meeting \#18 Minutes}\\
\end{center}
\end{adjustwidth}

18th Meeting (Friday, Week 9, 11:00, 6th October 2017)
\section{Attendance:}
\subsection*{Present}
\begin{itemize}
\item Adam Davidson, Cyrus Villacampa, James Kortman, Jeremy Hughes, Ravi Lam, Linlin Song, Ziang Chen
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item 
\end {itemize}

Meeting opened at 14:28
\section{Details:}
\begin{enumerate}
\item James has written a big list of things to be done.
\item We can’t go through the case study because the link is broken.
\item Line following discussion.
\item Localisation discussion.
\item Delay line following until small scale tests are done by Jeremy.
\item James to do No-go zone integration, coarse grid map interface, shape sensing because of map.
\item User provided location integration. Ziang UI map stuff. Fill in regions. Delay shape detection. Ravi will look at shape detection algorithm. Jeremy to do XML importing and exporting. James, implement multi-threading. James and Jeremy to co-work on mock robot.
\item Update timesheet on GitHub.
\item Write tests. Write comments.
\item Reminder to maintain/fix code style.
\item The case study. It sucks.
\end{enumerate}
Meeting closed 15:34.

\section{Action}
\begin{enumerate}
\item \textbf{Everyone} Do the case study.
\item \textbf{Everyone} Do next steps.
\end{enumerate}
\end{document}