\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Meeting \#13 Minutes}\\
\end{center}
\end{adjustwidth}


13th Meeting (Monday, Week 7, 2pm, 4th September 2017)
\section{Attendance:}
\subsection*{Present}
\begin{itemize}
\item Adam Davidson, Cyrus Villacampa, James Kortman, Jeremy Hughes, Ziang Chen, Ravi Lam, Ziang Chen, Linlin Song
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item 
\end {itemize}

Meeting opened at 14:12.
\section{Details:}
\begin{enumerate}
\subsection{SPMP Draft}
\item Linlin hasn’t done her section. She’ll do it this afternoon.
\item References fine
\item Definitions fine
\item People to add their own rationale behind their roles and responsibilities in Section 4. i.e. why you’re in that position.
\item Section 5 seems good.
\item Section 6 - the diagram could be tweaked to more match content given from lectures (Ravi)
\item Section 7 - Add gyroscope to sensor list
\item Ziang - Add a diagram for GitHub folder structure. Cyrus to try and move figure closer to text (Latex formatting).
\item We need to reassign the introduction. 1.3 - Adam. 1.1 - Cyrus. 1.2 - Jeremy. 1.4 Ziang. Aim to finish at 6pm so James can review.

\item Jeremy brought in the full sized (A1) trial map. It's a lot smaller than expected. That might change some of the algorithms etc.
\item Get the sensor functions working by Friday - Adam.
\end{enumerate}

\section{Action}
\begin{enumerate}
\item \textbf{Everyone} Work on their respective SPMP sections.
\item \textbf{James} Submit SPMP.
\item \textbf{Adam} Submit agenda for tomorrow.
\end{enumerate}


\end{document}