\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Meeting \#20 Minutes}\\
\end{center}
\end{adjustwidth}

20th Meeting (Friday, Week 10, 14:00, 13th October 2017)
\section{Attendance:}
\subsection*{Present}
\begin{itemize}
\item Adam Davidson, Cyrus Villacampa, James Kortman, Jeremy Hughes, Ravi Lam, Linlin Song, Ziang Chen
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item 
\end {itemize}

Meeting opened at 14:15.
\section{Details:}
\begin{enumerate}
\item Jeremy has looked over the case study and posted in Discord a list of 7 people who might be good to study. Get ready by Monday, present on Tuesday. 2-3 minute presentation on each character.
\item Status update. Jeremy has done some testing. XML stuff not done. Pathfinding being worked on. 
\item Meeting minutes missing. Jeremy will upload the two previous meetings’ minutes.
\item Sunday night goals: Automated turning commands not overshooting. Structure for XML importing. Shape sensing should be done. Path finding integration (end of Monday). UI real time display: Done, but not accurate. 
\item After Sunday: XML Exporting, shape detection.
\item Documents will wait until later.
\item Choose a person and post.
\end{enumerate}
Meeting closed 14:46.

\section{Action}
\begin{enumerate}
\item \textbf{Everyone} Pick a person and post on Discord who you've chosen.
\item \textbf{Everyone} Do the case study.
\item \textbf{Jeremy} Take the robot.
\item \textbf{Jeremy} Upload previous meetings minutes.
\end{enumerate}
\end{document}