\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Meeting \#12 Minutes}\\
\end{center}
\end{adjustwidth}


12th Meeting (Friday, Week 6, 2pm, 1st September 2017)
\section{Attendance:}
\subsection*{Present}
\begin{itemize}
\item Adam Davidson, Cyrus Villacampa, James Kortman, Jeremy Hughes, Ziang Chen, Ravi Lam, Ziang Chen, Linlin Song
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item 
\end {itemize}

Meeting started at 14:18

\section{Details:}
\begin{enumerate}
\item Is rendering the map hard? Image manipulation could be difficult. It'd be good to have a map demo (in the GUI), even if it doesn't work. We'll probably freeze the robot design in the break.
\item In the final SRS, we will need testing and errors in it.
\item Test cases are lacking in the code. To write test cases for the Robot class, it's basically the calibration documentation.
\item Use JavaDoc for everything. Look at labelling options. @see. JavaDoc also lacking a bit in the code. To (hopefully) solve code quality related issues, check these things before you push: Coding Style, JavaDoc everywhere. Also update any previous functions. \underline{Make sure nobody forks}.
\subsection{Milestones}
\item \textbf{Milestone 1} Sensor/verifying data from robot. Safe movement. Saving sensor data to data structure. Map demo. Client Meeting 4 map request. Send all sensor data. 
\item \textbf{Milestone 2} Mapping in real time and rendering the map. Path finding. Robot and Handler syncronisation (to fix any timing mismatches and potential errors.
\item \textbf{Final Milestones} Full autonomy. Map import/export

\end{enumerate}
Meeting closed at 15:16pm.


\section{Action}
\begin{enumerate}
\item \textbf{Everyone} Do your timesheets
\item \textbf{Everyone} Start of tomorrow: Post one or two sentence minimum for the SPMP.
\item \textbf{Everyone} Do tests for the code and familiarise with JUnit as necessary.
\item \textbf{Everyone} Sunday night midnight deadline for SPMP.
\item \textbf{James} By roughly Wednesday James will have a rough map API done.
\item \textbf{Jeremy} Test map from Jeremy by milestone 1. By Tuesday for the Client Meeting
\end{enumerate}


\end{document}