\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Meeting \#2 Minutes}\\
\end{center}
\end{adjustwidth}


Second Meeting (Thursday, Week 2, 3 August 2017)
\section{Attendance:}
\subsection*{Present}
\begin{itemize}
\item Adam Davidson, Cyrus Villacampa, James Kortman, Jeremy Hughes, Ravi Lam, Ziang Chen
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item Linlin Song
\end {itemize}

\section{Details:}
\begin{enumerate}
\item Agenda for initial client meeting – Cyrus had produced draft. Draft was read, and feedback and additional suggestions given. See Client Meeting Agenda (8 August 2017) for details.
\item Project architecture – discussed the different components requiring work for the product.
\item  Project roles – Looked over a list of potential roles to have on the team. Assigned some initial roles for what is immediately necessary, with the intention to assign further roles as required by the stage of the project.
\item Assigned Roles:
\begin{itemize}
\item Documentation Manager - Adam
\item Testing Manager - Ravi
\item Project/Communications Manger - Jeremy
\item Architecture Manager - James
\end{itemize}
\end{enumerate}

\section{Actions Points:}
\begin{enumerate}
\item Refine agenda for initial client meeting further (if necessary), and make sure group is ready for meeting (make sure anything else needing discussion before the meeting has been discussed, as well as appoint a chairman).
\item Finalize timing of regular group meetings.
\end{enumerate}

\end{document}