\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Meeting \#19 Minutes}\\
\end{center}
\end{adjustwidth}

19th Meeting (Monday, Week 10, 14:00, 9th October 2017)
\section{Attendance:}
\subsection*{Present}
\begin{itemize}
\item Cyrus Villacampa, James Kortman, Jeremy Hughes, Ravi Lam, Linlin Song, Ziang Chen
\end{itemize}
\subsection*{Apologies}
\begin{itemize}
\item Adam Davidson
\end {itemize}

Meeting opened at 14:15.
\section{Details:}
\begin{enumerate}
\item Requirements for next set of reviews discussed.
\item No progress on location precision for small motions.
\item Shape detection: Ravi investigating 2 libraries, discussion of using algorithm rather than library.
\item Decided on date for Final Presentation: Monday - 30th October 10:45-11:15.
\item Went back over the assigned roles for the rest of the work required.
\end{enumerate}

Meeting closed 14:55.

\section{Action}
For next week:
\begin{enumerate}
\item \textbf{Jeremy} Robot motion calibrated and tested, auto mode entirely working.
\item \textbf{Cyrus/Ravi/Ziang} Path finding integrated, ideally with GUI as well.
\item \textbf{Cyrus} Path finding sending auto move commands.
\item \textbf{James} Multithreading on Robot.
\item \textbf{James} Map improvements.
\item \textbf{Ziang} UI Real Time.
\item \textbf{Ziang} Objects being filled on GUI.
\item \textbf{Cyrus} to chair the next meeting.
\end{enumerate}

\end{document}