\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Meeting \#21 Minutes}\\
\end{center}
\end{adjustwidth}

21st Meeting (Monday, Week 11, 11:00, 16th October 2017)
\section{Attendance:}
\subsection*{Present}
\begin{itemize}
\item Adam Davidson, Cyrus Villacampa, James Kortman, Jeremy Hughes (late), Ravi Lam, Linlin Song, Ziang Chen
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item 
\end {itemize}

Meeting opened at 14:14
\section{Details:}
\begin{enumerate}
\item Path finding fully integrated with decision making and GUI provided location. Yet to be tested because lack of robot. UI map stuff no progress because lack of time (it’s okay). 
\item User manual, testing report is due week 12. For the testing report, just keep writing tests.
\item Small motion testing completed: It's not too bad. Seems plausible to do it on the Handler side. 
\item Code base features to be done (roughly by the end of the week): XML importing and exporting, shape sensor (passes tests, not yet fully tested), path finding testing, line following mode (biggest task), high level decision making (i.e. to swap between line following, going to location etc), UI real time stuff. Try multithreading (maybe).
\item Shape detection looks potentially difficult. Some strategies discussed. 
\item Adam will chair tomorrow. Only question: Are craters guaranteed to be black?
\item We may get a reference reading on the day and enter it in settings.
\item User manual - Ziang and Adam. Hopefully find a template for it.
\end{enumerate}
Meeting closed 14:35.

\section{Action}
\begin{enumerate}
\item \textbf{Everyone} Prepare for case study presentation.
\item \textbf{Everyone} Work on respective sections.
\item \textbf{Cyrus, James} Line following algorithm.
\item \textbf{Ziang, Adam} Do user manual.
\item \textbf{Jeremy} Update robot code descriptions and robot tests.
\end{enumerate}
\end{document}