\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Meeting \#1 Minutes}\\
\end{center}
\end{adjustwidth}


Initial Meeting (Monday, Week 2, 31 July 2017)
\section{Attendance:}
\subsection*{Present}
\begin{itemize}
\item Adam Davidson
\item Cyrus Villacampa
\item James Kortman
\item Jeremy Hughes
\item Ravi Lam
\item Ziang Chen
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item Linlin Song
\end {itemize}

\section{Details:}
\begin{enumerate}
\item Discord was suggested, and set up during the meeting, to facilitate communication.
\item To work on LaTeX documents, overleaf.com is suggested. A brief rundown of how Latex works.
\item Trello suggested if we need lists for collaboration.
\item Experience discussed - a few members had some Java experience, plus one member studying Mechatronic/Mechanical Engineering.
\item Time for future meeting discussed - Adam to investigate using Doodle to mark availabilities.
\item Decision to include all documents on Github to keep track of them, and allow versioning.
\end{enumerate}

\section{Actions Points:}
\begin{enumerate}
\item Query lecturers about: Github repositories, Client specification, Requirements for first client meeting, Group Roles, Tex files for document templates.
\item Organise additional meeting times via Discord
\item Adam to get template documents in Latex format
\end{enumerate}

\end{document}