\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
\usepackage{changepage}
\begin{document}
\begin{adjustwidth}{2.5em}{0pt}
\begin{center}
\Large{UG 12 Meeting \#6 Minutes}\\
\end{center}
\end{adjustwidth}
\justify

Sixth Meeting (Monday, Week 4, 14 August 2017)
\section{Attendance:}
\subsection*{Present}
\begin{itemize}
\item Adam Davidson, Cyrus Villacampa, James Kortman, Jeremy Hughes, Ziang Chen, Ravi Lam, Ziang Chen
\end{itemize}
\subsection*{Absent}
\begin{itemize}
\item Linlin Song
\end {itemize}

\section{Details:}
\begin{enumerate}
\item We have a client meeting tomorrow. We're done with the requirement solicitation from last
meeting, so we probably won't need to ask many more questions about that.
Division of responsibilities: Assigned roles. Not everyone has a role, but that's part of our
agile programming paradigm. Selection of process model: We aim to get something workable
and iterating implementation from there. Frequent prototyping. Agile programming
For the client meeting tomorrow: Chair - Jeremy. Minute taker - Adam
Adam will check the requirements of documents and types, especially Latex and minutes
Process for handling evolving requirements and documents:
Do we have a project manager? It's been vague. James/Jeremy are co-Project Managers
\item Timeline\\
We need a timeline:\\
Week 4:\\
Week 5:\\
Week 6: Basic movement and remote control through GUI\\
Week 7:\\
Week 8:\\
Mid 1:\\
Mid 2:\\
Week 9: DTD\\
Week 10:\\
Week 11:\\
Week 12:\\
Check timetable online and complete timeline [Adam]\\
\item Adam worked on the robot over the weekend and loaded software onto the Robot and Eclipse
and got the large motors, medium motors, color sensor and touch sensor working. The mo-
tors seem to be accurate.\\
Where does the code for the robot run? Robot or computer?\\
We'll need to use different threads for different things to make sure\\
Communications for the robot have been replaced.\\
\item Rough Agenda for tomorrow (client meeting \#2):\\
Project readiness\\
Show current progress - including GUI\\
Possible questions: Dimensions of NGZ. Are they retangular?\\

\item We have two sets of folders in GitHub. That may need to be one folder.

\item We will need to complete a risk analysis at some stage.

\item We will need to implement testing functions. For the robot, we won't necessarily do unit
tests, but do more calibrating tests with the robot.\\
Meeting closed at 3

\end{enumerate}

\section{Action}
\begin{enumerate}
\item Put your stuff on GitHub
\item Read up on agile programming definitions
\item Adam to do a timeline
\item Adam will check the requirements of documents and types, especially Latex and minutes

\end{enumerate}


\end{document}